\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-03-18 docs/parco13/abstract.tex
Add a forest picture

\usepackage{amsmath,amssymb}
\usepackage{cite}
\usepackage{color}
\usepackage{url}
\usepackage{xspace}

@@

The MPI layer is addressed from within \pforest and not exposed to the
\forestclaw code.  The order of leaves is maintained in \pforest according to a
space filling curve.  Each MPI rank has a local view on its own partition,
augmented where necessary with information about one layer of ghost leaves.

>>>>

\usepackage{amsmath,amssymb}
\usepackage{cite}
\usepackage{color}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}

@@

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{../figs_misc/cubed3}
\caption{The leaves in a forest of six octrees that serves as the computational
domain for the cubed sphere.  An adhoc refinement pattern has been 2:1 balanced
in terms of neighbor sizes and partitioned between five MPI processes (the
three middle ones are shown from black to white).}
\label{cubed3}
\end{figure}

The MPI layer is addressed from within \pforest and not exposed to the
\forestclaw code.  The order of leaves is maintained in \pforest according to a
space filling curve.  Each MPI rank has a local view on its own partition,
augmented where necessary with information about one layer of ghost leaves
(see Figure~\ref{cubed3}).
